---
title: "Lab3"
author: "Michelle Hernandez"
format: html
editor: visual
---

## Quarto

1.  Read in the data

```{r}
download.file(
  "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
  destfile = file.path("~", "Downloads", "met_all.gz"),
  method   = "libcurl",
  timeout  = 60
)

met <- data.table::fread(file.path("~", "Downloads", "met_all.gz"))

```

Question2

```{r}
dim(met)
head(met)
tail(met)


```

Question3

```{r}
str(met)
```

Question4

```{r}
table(met$year)
table(met$day)
table(met$hour)

summary(met$temp)
summary(met$elev)
summary(met$wind.sp)

met[met$elev==9999.0] <- NA
summary(met$elev)

met <- met[temp>-40]
met2 <- met[order(temp)]
head(met2)

met[met$temp==-17.2,]
# yoder colorado, prob doesnt get that cold so we should remove


```

Question5

```{r}
met <- met[temp>-15]
met2 <- met[order(temp)]
head(met2)
summary(met$temp)
# We removed any entries with a temp > -15, our lowest temp is now -3C which is resonable



```

Question6

```{r}
eleview <- met[elev==max(elev), ]
summary(eleview)

cor(eleview$temp, eleview$wind.sp, use="complete")
cor(eleview$temp, eleview$hour, use="complete")
cor(eleview$wind.sp, eleview$day, use="complete")
cor(eleview$wind.sp, eleview$hour, use="complete")
cor(eleview$temp, eleview$day, use="complete")
```

Question7

```{r}
hist(met$elev, breaks=100)
hist(met$temp)
hist(met$wind.sp, breaks=100)

leaflet(eleview) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)
library(lubridate)
eleview$date <- with(eleview, ymd_h(paste(year, month, day, hour, sep= ' ')))
summary(eleview$date)

eleview <- eleview[order(date)]
head(eleview)

plot(eleview$date, eleview$temp, type='l')

plot(eleview$date, eleview$wind.sp, type='l')
```

Question8 - Further Analysis

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
